One-stage point transect distance sampling using iterated integrated nested Laplace approximations

### 2024-10-30 paper.tex
start converting figures to pdf + final tweaks

@@

@@

\begin{figure}[!htb]
	\centering
	\includegraphics[scale=0.5]{figures/study_area_design.png}
	\caption{Study area showing the 2002 survey points (black dots) in Hakalau Forest National Wildlife Refuge, \hawaii{} Island.  Eastings and Northings are in kilometres.}
	\label{fig:2002studyareapointspt}
\end{figure}

@@

The predicted mean of the posterior intensity field is shown in \autoref{fig:intensity-mean-cv}A along with a map of the coefficient of variation (CV) (\autoref{fig:intensity-mean-cv}B) and standard deviation of the posterior intensity field (\autoref{fig:intensity-mean-cv}C) on a regular prediction grid with each prediction cell area approximately 1.7 hectares.
\begin{figure}[!htb]
	\begin{center}
		\includegraphics[scale=0.525]{figures/intensity_mean_cv_sd.png}
		\caption{The A) mean, B) CV and C) SD of the posterior intensity field.  Units are per m$^2$.  The colour scale is different for each panel.}
		\label{fig:intensity-mean-cv}
	\end{center}
\end{figure}
This shows a region of high intensity in the south and much lower intensity in the north, agreeing with a standard two-stage analysis of the same data \citep{camp_dsm_2020}.  The CV plot shows that the CV in the posterior intensity field is lower in areas with greater sampling effort and higher intensity.  There is a clear indication of preferential sampling with more survey effort in the south, where densities are higher, compared to the north.  In the north, estimated intensities are lower, which also contributes to larger CV values and makes the CV map hard to interpret.  The standard deviation map shows stronger overall posterior variability in the south where intensity is larger, most likely due to the assumed log-normal relationship between the random field and the Poisson rate parameter.

@@

The posterior detection function (\autoref{fig:det-matern}) shows that detectability drops to just under 0.25 at the maximum observable distance of 58 metres and also broadly agrees with a two-stage analysis.
\begin{figure}[!htb]
	\begin{center}
		\includegraphics[scale=0.525]{figures/detfn_and_matern.png}
		\caption{A) Posterior half-normal detection function. B) Posterior Mat\'ern correlation function.  The black line is the mean posterior estimate and the grey shaded area is 95\% credible interval in both plots}
		\label{fig:det-matern}
	\end{center}
\end{figure}
The posterior Mat\'ern correlation function is shown in \autoref{fig:det-matern}; the grey regions show the 95\% credible interval.  We note that this correlation function shows positive correlation even at distances of 10,000 metres, wider than the full length of the study region (approximately 8,000 metres).  This is because the correlation function is defined on the log-intensity scale.  On the intensity scale the empirical range of correlation is shorter.

>>>>

% to find textwidth
%\usepackage{layouts}

@@

Text width here we go:
%\printinunitsof{cm}\prntlen{\textwidth}

@@

\begin{figure}[!htb]
	\centering
	\includegraphics{figures/study_area_design.pdf}
	\caption{Study area showing the 2002 survey points (black dots) in Hakalau Forest National Wildlife Refuge, \hawaii{} Island.  The red outline marks the study area boundary as defined in \cite{camp_dsm_2020}.}
	\label{fig:2002studyareapointspt}
\end{figure}

@@

The predicted mean of the posterior intensity field is shown in \autoref{fig:intensity-mean-cv}A along with a map of the coefficient of variation (CV) (\autoref{fig:intensity-mean-cv}B) and standard deviation of the posterior intensity field (\autoref{fig:intensity-mean-cv}C) on a regular prediction grid with each prediction cell area approximately 1.7 hectares.
\begin{figure}[!htb]
	\begin{center}
		\includegraphics[width=\textwidth]{figures/intensity_mean_cv_sd.pdf}
		\caption{The A) mean, B) CV and C) SD of the posterior intensity field.  Units are per m$^2$.  The colour scale is different for each panel.}
		\label{fig:intensity-mean-cv}
	\end{center}
\end{figure}
This shows a region of high intensity in the south and much lower intensity in the north, agreeing with a standard two-stage analysis of the same data \citep{camp_dsm_2020}.  The CV plot shows that the CV in the posterior intensity field is lower in areas with greater sampling effort and higher intensity.  There is a clear indication of preferential sampling with more survey effort in the south, where densities are higher, compared to the north.  In the north, estimated intensities are lower, which also contributes to larger CV values and makes the CV map hard to interpret.  The standard deviation map shows stronger overall posterior variability in the south where intensity is larger, most likely due to the assumed log-normal relationship between the random field and the Poisson rate parameter.

@@

The posterior detection function (\autoref{fig:det-matern}) shows that detectability drops to just under 0.25 at the maximum observable distance of 58 metres and also broadly agrees with a two-stage analysis.
\begin{figure}[!htb]
	\begin{center}
		\includegraphics[width=\textwidth]{figures/detfn_and_matern.pdf}
		\caption{A) Posterior half-normal detection function. B) Posterior Mat\'ern correlation function.  The black line is the mean posterior estimate and the grey shaded area is 95\% credible interval in both plots}
		\label{fig:det-matern}
	\end{center}
\end{figure}
The posterior Mat\'ern correlation function is shown in \autoref{fig:det-matern}; the grey regions show the 95\% credible interval.  We note that this correlation function shows positive correlation even at distances of 10,000 metres, wider than the full length of the study region (approximately 8,000 metres).  This is because the correlation function is defined on the log-intensity scale.  On the intensity scale the empirical range of correlation is shorter.
